\documentclass[11pt,a4paper]{article}

\usepackage[margin=1in]{geometry}
\usepackage{xcolor}
\usepackage{listings}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage{booktabs}

\definecolor{bgshade}{HTML}{F7F2EA}
\definecolor{bdr}{HTML}{E2DBCE}
\definecolor{acc}{HTML}{9A7040}
\definecolor{tx2}{HTML}{524A40}
\definecolor{tx3}{HTML}{948B81}
\definecolor{red}{HTML}{B83232}
\definecolor{green}{HTML}{387038}

\hypersetup{
  colorlinks=true,
  linkcolor=acc,
  urlcolor=acc
}

\lstset{
  backgroundcolor=\color{bgshade},
  basicstyle=\ttfamily\footnotesize,
  breaklines=true,
  frame=single,
  rulecolor=\color{bdr},
  framesep=6pt,
  xleftmargin=10pt,
  xrightmargin=4pt,
  showstringspaces=false,
  keywordstyle=\color{acc}\bfseries,
  commentstyle=\color{tx3}\itshape,
  stringstyle=\color{green}
}

\titleformat{\section}{\Large\bfseries\color{acc}}{\thesection.}{0.6em}{}
\titleformat{\subsection}{\large\bfseries\color{tx2}}{\thesubsection.}{0.5em}{}

\title{\textbf{Studio OS --- Session Change Log}\\[4pt]
  \large Duplicate-Contacts Fix, Database Cleanup, and UX Polish}
\author{Working directory: \texttt{/Users/putla\_theophila/Desktop/studios}}
\date{2026-05-19}

\begin{document}
\maketitle

\section{Summary}

Three threads of work landed in this session:

\begin{enumerate}[leftmargin=*]
  \item \textbf{Duplicate-contacts bug.} The \texttt{/api/import} POST endpoint
        could create multiple rows for the same person because
        (a) the sourcing loop had no de-duplication and
        (b) no check ran against the existing contacts table at insert time.
        Fixed at both the API and the dialog layer.
  \item \textbf{Database cleanup.} Two duplicate contact pairs that already
        existed in production were merged in-place, with foreign-key
        references rewritten to the survivors.
  \item \textbf{UX polish.} Replaced blocking \texttt{alert()}/\texttt{confirm()}
        calls with a non-blocking toast stack and a styled confirm dialog.
        Added a search-bar icon, clear-button, and card hover-lift.
        No structural changes to existing pages.
\end{enumerate}

\hrule
\bigskip

\section{Duplicate Contacts --- Root Cause and Fix}

\subsection{Root cause}

In \texttt{src/app/api/import/route.ts} (POST handler):

\begin{itemize}[leftmargin=*]
  \item The \emph{sourcing} branch unconditionally pushed every selected POC
        into \texttt{newContacts}, so two sourcing rows with the same
        \texttt{poc\_name} produced two contacts.
  \item The \emph{events} and \emph{content} branches deduped against
        the in-memory \texttt{newContacts} array, but \emph{not} against the
        existing \texttt{contacts} table. The GET filter that hides imported
        POCs could race with stale React Query cache, allowing the same item
        to be selected and re-inserted.
  \item The \texttt{ImportDialog} client component had no \texttt{importing}
        guard, so a double-click on \emph{Import Selected} fired two POSTs.
\end{itemize}

\subsection{API-side fix}

\textbf{File:} \texttt{src/app/api/import/route.ts}

Pre-fetched existing contact names into a \texttt{taken} set, then routed
every insert through a single \texttt{tryAdd(name, payload)} helper that
skips empties, names already in the database, and intra-batch duplicates
across all three sources:

\begin{lstlisting}[language=Java]
const { data: existingContacts } = await supabase
  .from('contacts').select('name');
const taken = new Set(
  (existingContacts || []).map(c => (c.name || '').toLowerCase())
);

const tryAdd = (name, payload) => {
  const k = (name || '').trim().toLowerCase();
  if (!k || taken.has(k)) return;
  taken.add(k);
  newContacts.push(payload);
};
\end{lstlisting}

The sourcing, events, and content loops now all call \texttt{tryAdd(...)}
instead of pushing directly.

\subsection{Client-side fix}

\textbf{File:} \texttt{src/app/contacts/ContactsClient.tsx}

Added an \texttt{importing} state to \texttt{ImportDialog} so the
\emph{Import Selected} button is disabled while the request is in flight
and shows \emph{Importing\ldots}. The Cancel button is also disabled
during the request to prevent a stale close.

\hrule
\bigskip

\section{Live Database Cleanup}

Ran SQL via the Supabase Management API
(project \texttt{glbhstjsdtgiblppvlaq}) to merge pre-existing duplicates.

Found two duplicate groups, both with two rows each:

\begin{lstlisting}[language=SQL]
SELECT lower(name) AS k, count(*) AS n
FROM contacts
GROUP BY lower(name)
HAVING count(*) > 1;
-- Returned: theo (2), theophila (2)
\end{lstlisting}

Inside a transaction:

\begin{enumerate}[leftmargin=*]
  \item For each duplicate group, chose the \emph{earliest}
        \texttt{created\_at} row as the canonical \emph{keeper}.
  \item Re-pointed \texttt{poc\_contact\_id} on
        \texttt{sourcing\_records}, \texttt{events}, and
        \texttt{content\_items} from the loser id to the keeper id.
  \item Deleted the loser rows.
\end{enumerate}

\begin{lstlisting}[language=SQL]
BEGIN;
UPDATE sourcing_records s SET poc_contact_id = r.keeper
FROM (
  SELECT id AS loser,
         FIRST_VALUE(id) OVER (
           PARTITION BY lower(name)
           ORDER BY created_at, id
         ) AS keeper
  FROM contacts
) r
WHERE s.poc_contact_id = r.loser AND r.loser <> r.keeper;
-- repeat for events and content_items

DELETE FROM contacts WHERE id IN (
  SELECT id FROM (
    SELECT id, ROW_NUMBER() OVER (
      PARTITION BY lower(name) ORDER BY created_at, id
    ) AS rn FROM contacts
  ) x WHERE rn > 1
);
COMMIT;
\end{lstlisting}

\textbf{Result:} duplicate-count query returns zero rows; total contacts
collapsed from four to two.

\hrule
\bigskip

\section{UX Polish --- Toast and Confirm}

\subsection{New components}

\subsubsection*{\texttt{src/components/Toast.tsx} \textit{(new)}}

A module-level event store with an attached \texttt{<ToastViewport />}
React component. Public API:

\begin{lstlisting}[language=Java]
import { toast } from '@/components/Toast';

toast.success('Contact updated');
toast.error('Save failed');
toast.info('...');
\end{lstlisting}

Toasts auto-dismiss (3.8s default, 5.2s for errors), stack
bottom-right, animate in, and can be dismissed manually via an
\texttt{IconClose} button. Each kind (success / error / info) has its own
colour, inline SVG icon, and ARIA role
(\texttt{alert} for errors, \texttt{status} otherwise).

\subsubsection*{\texttt{src/components/Confirm.tsx} \textit{(new)}}

Imperative, promise-based replacement for \texttt{window.confirm}:

\begin{lstlisting}[language=Java]
import { confirmDialog } from '@/components/Confirm';

const ok = await confirmDialog({
  title: 'Delete record',
  message: 'This will permanently remove this sourcing record...',
  confirmLabel: 'Delete',
  destructive: true
});
if (!ok) return;
\end{lstlisting}

Keyboard support: \texttt{Esc} cancels, \texttt{Enter} confirms,
\texttt{autoFocus} lands on the safe button by default
(or the destructive button when \texttt{destructive: true} so deliberate
typing isn't required, but click confirmation still is).
Falls back to \texttt{window.confirm} if mounted before
\texttt{ConfirmHost}.

\subsection{Provider wiring}

\textbf{File:} \texttt{src/components/QueryProvider.tsx}

Mounted both hosts inside the existing \texttt{QueryClientProvider} so
that every feature page (sourcing, contacts, calendar, events) inherits
them without changing each page file.

\begin{lstlisting}[language=Java]
return (
  <QueryClientProvider client={client}>
    {children}
    <ToastViewport />
    <ConfirmHost />
  </QueryClientProvider>
);
\end{lstlisting}

\subsection{Styling}

\textbf{File:} \texttt{src/app/globals.css}

Added three blocks:

\begin{itemize}[leftmargin=*]
  \item \texttt{.toast-stack} / \texttt{.toast} +
        \texttt{@keyframes toastIn} --- positioning, motion, layered shadow.
  \item \texttt{.card-tap} --- subtle translateY hover-lift utility for
        clickable cards.
  \item \texttt{.skeleton} + \texttt{@keyframes shimmer} ---
        ready for future loading states.
\end{itemize}

\hrule
\bigskip

\section{Replacements --- \texttt{alert/confirm} $\to$ Toast/Confirm}

Every blocking call in the client tree was replaced. Successful
write paths now also emit a positive \texttt{toast.success(...)} so the
user gets confirmation, not silence.

\begin{center}
\begin{tabular}{ll}
\toprule
\textbf{File} & \textbf{Replacement} \\
\midrule
\texttt{contacts/ContactsClient.tsx} & 3 alerts $\to$ toast + success on save \& import \\
\texttt{sourcing/SourcingForm.tsx}   & 2 alerts + 1 confirm $\to$ toast + \texttt{confirmDialog} \\
\texttt{sourcing/SourcingDetail.tsx} & 1 alert $\to$ toast (status-change success) \\
\texttt{events/EventsClient.tsx}     & 2 alerts $\to$ toast + success on save \\
\texttt{calendar/CalendarClient.tsx} & 3 alerts $\to$ toast + success on save \\
\bottomrule
\end{tabular}
\end{center}

The destructive \emph{Remove this record} prompt in
\texttt{SourcingForm.tsx} now reads:

\begin{lstlisting}[language=Java]
const ok = await confirmDialog({
  title: 'Delete record',
  message: 'This will permanently remove this sourcing record. ' +
           'This cannot be undone.',
  confirmLabel: 'Delete',
  destructive: true
});
\end{lstlisting}

\hrule
\bigskip

\section{Smaller Polish}

\subsection{Contacts search input}

\textbf{File:} \texttt{src/app/contacts/ContactsClient.tsx}

\begin{itemize}[leftmargin=*]
  \item Leading \texttt{IconSearch} positioned inside the input.
  \item Inline \emph{Clear} (\texttt{IconClose}) button appears when the
        query is non-empty.
  \item Padding adjusted (\texttt{padding-left: 34px}) to accommodate the
        leading icon.
\end{itemize}

\subsection{Card hover-lift}

Applied the new \texttt{.card-tap} class to:

\begin{itemize}[leftmargin=*]
  \item Contact cards in \texttt{ContactsClient.tsx}.
  \item Event cards in \texttt{EventsClient.tsx}.
\end{itemize}

The class drives a 1px upward \texttt{translate} and a soft shadow on
hover, with motion governed by the existing global
\texttt{--ease} / \texttt{--t} tokens.

\subsection{Stale emoji-to-SVG residue}

Two lingering references to a removed \texttt{stars()} util in
\texttt{events/EventsClient.tsx} were resolved:

\begin{itemize}[leftmargin=*]
  \item Line 136 (badge): replaced with
        \texttt{<Stars n=\{event.importance\} size=\{11\} />}.
  \item Line 277 (\texttt{<option>} text, where SVG can't render):
        replaced with Unicode
        \texttt{'\textbackslash u2605'.repeat(i) + '\textbackslash u2606'.repeat(5 - i)}.
\end{itemize}

\hrule
\bigskip

\section{Files Touched}

\begin{center}
\begin{tabular}{ll}
\toprule
\textbf{Path} & \textbf{Kind} \\
\midrule
\texttt{src/components/Toast.tsx}                & new \\
\texttt{src/components/Confirm.tsx}              & new \\
\texttt{src/components/QueryProvider.tsx}        & wired hosts \\
\texttt{src/app/globals.css}                     & toast, skeleton, card-tap \\
\texttt{src/app/api/import/route.ts}             & dedupe via \texttt{tryAdd} \\
\texttt{src/app/contacts/ContactsClient.tsx}     & toasts, search polish, hover-lift \\
\texttt{src/app/sourcing/SourcingForm.tsx}       & toasts, \texttt{confirmDialog} \\
\texttt{src/app/sourcing/SourcingDetail.tsx}     & toasts \\
\texttt{src/app/events/EventsClient.tsx}         & toasts, hover-lift, Stars fix \\
\texttt{src/app/calendar/CalendarClient.tsx}     & toasts \\
\midrule
\textbf{Live database} & 2 duplicate pairs merged, FKs repointed \\
\bottomrule
\end{tabular}
\end{center}

\hrule
\bigskip

\section{Verification}

\begin{itemize}[leftmargin=*]
  \item \texttt{npx tsc --noEmit} --- clean, no diagnostics.
  \item Post-cleanup duplicate query --- returns zero rows.
  \item Existing component structure preserved across all feature pages.
\end{itemize}

\end{document}
